Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2018-05-22 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
changed to the TeX file for MST1 23 of May including the comments on the work of Matteo and Daniel

\begin{frame}{Current scan at constant q$_{95}$}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG peak target density rollover
          occurs at lower density for lower current as well as
          radiation front movement. For TCV rollover achieved only at
          higher current: \alert{lower I$_p$ does not exhibit sign of
          detachment even if high density is
          achieved. Consistent with lower 
            volumetric recombination from DSS}
         \item<only@5> Interestingly considering the behavior as a
           function of greenwald fraction does not reconcile the
           different current neither on AUG.  
        \only<6-7>{\item For AUG upstream and target profiles still
          exhibit flattening earlier in density at lower current but
          \alert{always at large values of 
          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
          at very large values of $\Lambda_{div}$}
        \item<only@7>  This is due to the fact we did not reach
          divertor detachment which \alert{seems mandatory for
            upstream profile modification}}  
        \item<only@8> AUG: Amplitude evolution as a function of
          greenwald fraction confirms that shoulder starts appearing
          at the onset of highly recycling regime 
        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<only@10> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<only@11> And for TCV this is true even at high value of
          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
          guarantee flat profiles on TCV.}
% % %% H-Mode same fueling
\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
  \begin{column}{0.45\textwidth}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as} \textcolor{colorA}{\# 34276}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump

>>>>

\begin{frame}{Current scan at constant q$_{95}$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan even
          though this required for TCV operation with very low
          toroidal field (0.8T)
        \item<1|only@1> The parallel connection length remains almost unchanged
        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
          pretty reproducible behavior matching basically the plasma
          condition in within the current scan
        \item<3|only@3> TCV: Even at such an high density at lower
          current (and lower B$_t$) no sign of target ion flux
          rollover/detachment
        \item<4|only@4> AUG peak target density rollover
          occurs at lower density for lower current as well as
          radiation front movement. For TCV rollover achieved only at
          higher current: \alert{lower I$_p$ does not exhibit sign of
          detachment even if high density is
          achieved. Consistent with lower 
            volumetric recombination from DSS}
         \item<only@5> Interestingly considering the behavior as a
           function of greenwald fraction does not reconcile the
           different current neither on AUG.  
        \only<6-7>{\item For AUG upstream and target profiles still
          exhibit flattening earlier in density at lower current but
          \alert{always at large values of 
          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
          at very large values of $\Lambda_{div}$}
        \item<only@7>  This is due to the fact we did not reach
          divertor detachment which \alert{seems mandatory for
            upstream profile modification}}  
        \item<only@8> AUG: Amplitude evolution as a function of
          greenwald fraction confirms that shoulder starts appearing
          at the onset of highly recycling regime 
        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
          still reconcile the explored current scan
        \item<only@10> AUG exhibit consistently an increase of
          $\lambda_n$ with blob-size whereas for TCV the profile
          remains flat consistently with a small variation of
          $\delta_b$
        \item<only@11> And for TCV this is true even at high value of
          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
          guarantee flat profiles on TCV.}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Neutral behavior investigation on AUG: M. Agostini}
  \only<1>{
    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}
          \item Light emission analysis performed using 2 absolute
            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
            filter
          \item Tomographic inversion using pixel technique assuming
            emission only outside the LCFS and neglecting reflection
          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
            \textbf{R}econstruction \textbf{T}echnique (SART) with no
            input from equilibrium and no regolarization
          \item Evolution during density ramp explored
        \end{itemize}
      \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
      \end{column}
    \end{columns}
  }
  \only<2>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
    At the beginning of the fueling ramp emission localized in the HFS
  }
  \only<3>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
Radiation starts moving along the separatrix with different patterns between the two radiation
  }
  \only<4>{
    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
    Emission propagate also towards the LFS and moves towards the CFR
  }
\end{frame}

\begin{frame}{Heat transport and power balance: D. Carralero}
  \only<1>{
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item Using a large database (around 30 discharges) in
          L-Mode detailed ion and electron temperature profiles
          collected
        \item Consistent ion temperature drop observed whenever shoulder
          is observed
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Carralero_ionTemperature}
    \end{column}
  \end{columns}
}
\only<2>{
  \centering{\includegraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
  \Fontvi
  \begin{itemize}
    \item Parallel heat flux dominated by ion conduction whereas
      perpendicular component dominated by ion convection
    \item In high density regime a substantial fraction of
      P$_{\mathrm{SOL}}$ still remains in the $Q_{\perp}$ for
      $r-r_{\mathrm{LCFS}} \sim 20$ cm
  \end{itemize}
}
\end{frame}
% % %% H-Mode same fueling
\begin{frame}{H-Mode analysis on AUG}
    \Fontvi
  \vspace{-1cm}
  \begin{columns}
  \begin{column}{0.55\textwidth}
    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
  \end{column}
  \begin{column}{0.45\textwidth}
    \begin{itemize}
    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
      total heating power where we changed the fueling and the
      efficiency of cryopumps. Specifically we have
      \begin{itemize}
        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
            cryompumps}
        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}
        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
            fueling and seeding trying to mimic the same subdivertor
            pressure as} \textcolor{colorA}{\# 34276}
      \end{itemize}
    \item<1|only@1> Keeping the same fueling with the cryopump clearly
      reduce the pressure in the the sub-divertor area, we don't reach
      clear detachment and the edge density is constant even during
      the fueling ramp. Degraded H-mode reached later without the cryopump
